KidsAIR: Main analysis

### 2021-02-26 main_analysis_final.Rmd
Various analysis updates to help with primary manuscript

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 23 Dec 2020"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+"))) 
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total),
         child_age = factor(child_age, levels = c("< 1", "1+")))

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+"))) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+"))) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

analysis_data_noak <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+"))) %>% 
  filter(area != "AK")
```

@@

int_function(analysis_data, "residents_smoke")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

@@

int_function(analysis_data_winter1, "burn_level_3level")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

# Try: home_floors_2level, home_sqft_2level, education_3level, child_age
# home_year_built_2level, stove_age_3level, stove_grade_3level, chimney_clean_3level,
# wood_collect_2level, wood_collect_method_2level, burn_level_3level, residents_smoke

@@

@@

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ filter_compliance + 
                                  child_age + (1 | cohort:area), 
                                  data = analysis_data_winter1)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
#itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
#itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
#itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_noak_tidy, itt_pm_income_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

ITT Primary = Linear mixed model, as specified above  
ITT no AK = Primary model without homes from AK (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period

@@

er_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*int_var + 
                          child_age + 
                          education_3level + 
                          #residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(er_results_int)

@@

lrti_summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_winter),
         lrti_events_num = lrti_events_num - 1) %>%  
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)

@@

int_function(analysis_data_winter1, "residents_smoke")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

@@

er_income_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          residents_smoke + person_time_at_risk_winter + 
                          income_3level + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_income_results, paste0(file_path, "Output/er_income_results.rds"))

er_filter_comp_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter + 
                          kw_perc_exp_cat2 + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_filter_comp_results, paste0(file_path, "Output/er_filter_comp_results.rds"))

er_burn_level_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter + 
                          burn_level_3level + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_burn_level_results, paste0(file_path, "Output/er_burn_level_results.rds"))

er_smoking_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + person_time_at_risk_winter + 
                          home_act_smoking_sum + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_smoking_results, paste0(file_path, "Output/er_smoking_results.rds"))

er_windows_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter + 
                          home_act_windows_sum + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_windows_results, paste0(file_path, "Output/er_windows_results.rds"))

er_door_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter + 
                          home_act_door_sum + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_door_results, paste0(file_path, "Output/er_door_results.rds"))

er_sweep_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter +
                          home_act_sweep_sum + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_sweep_results, paste0(file_path, "Output/er_sweep_results.rds"))

er_ambpm_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter +
                          amb_pm_lrti + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_ambpm_results, paste0(file_path, "Output/er_ambpm_results.rds"))

er_ambtemp_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          income_3level + residents_smoke + person_time_at_risk_winter +
                          amb_temp_lrti + 
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
write_rds(er_ambtemp_results, paste0(file_path, "Output/er_ambtemp_results.rds"))
```

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_income_results <- read_rds(paste0(file_path, "Output/er_income_results.rds"))
#er_filter_comp_results <- read_rds(paste0(file_path, "Output/er_filter_comp_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_smoking_results <- read_rds(paste0(file_path, "Output/er_smoking_results.rds"))
er_windows_results <- read_rds(paste0(file_path, "Output/er_windows_results.rds"))
er_door_results <- read_rds(paste0(file_path, "Output/er_door_results.rds"))
er_sweep_results <- read_rds(paste0(file_path, "Output/er_sweep_results.rds"))
er_ambpm_results <- read_rds(paste0(file_path, "Output/er_ambpm_results.rds"))
er_ambtemp_results <- read_rds(paste0(file_path, "Output/er_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_income_tidy <- results_function(er_income_results, "ER + income")
#er_filter_comp_tidy <- results_function(er_filter_comp_results, "ER + filt comp")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_smoking_tidy <- results_function(er_smoking_results, "ER + smoke act")
er_windows_tidy <- results_function(er_windows_results, "ER + window act")
er_door_tidy <- results_function(er_door_results, "ER + door act")
er_sweep_tidy <- results_function(er_sweep_results, "ER + sweep act")
er_ambpm_tidy <- results_function(er_ambpm_results, "ER + amb PM")
er_ambtemp_tidy <- results_function(er_ambtemp_results, "ER + amb temp")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_income_tidy, er_burn_level_tidy, 
                              er_smoking_tidy, er_windows_tidy, er_door_tidy,
                              er_sweep_tidy, er_ambpm_tidy, er_ambtemp_tidy)

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 26 Feb 2021"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) 
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")))

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

analysis_data_noak <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(area != "AK")
```

@@

int_function(analysis_data, "home_sqft_2level")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

@@

int_function(analysis_data_winter1, "stove_grade_3level")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

# Try: home_floors_2level, home_sqft_2level, education_3level, child_age
# home_year_built_2level, stove_age_3level, stove_age_di, stove_grade_3level, chimney_clean_3level,
# wood_collect_2level, wood_collect_method_2level, burn_level_3level, residents_smoke

@@

itt_pm_at_home_results <- glmer(log(pm_mean_at_home_sampling_period) ~ treatment_assigned + 
                               child_age + (1 | cohort:area), 
                               data = analysis_data_winter1)
write_rds(itt_pm_at_home_results, paste0(file_path, "Output/itt_pm_at_home_results.rds"))

@@

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ filter_compliance + 
                                  child_age + (1 | cohort:area), 
                                  data = analysis_data_winter1)
summary(itt_pm_filter_comp_results)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

@@

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_at_home_results <- read_rds(paste0(file_path, "Output/itt_pm_at_home_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_at_home_tidy <- results_function(itt_pm_at_home_results, "ITT PM at-home")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
#itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_at_home_tidy, itt_pm_noak_tidy, itt_pm_income_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT PM at-home", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM outcome") +
  labs(y = "% difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

ITT Primary = Linear mixed model, as specified above  
ITT PM at-home = Primary model using PM when child was at home  
ITT no AK = Primary model without homes from AK (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period

@@

er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr*int_var + 
                          #child_age + 
                          gender + 
                          residents_smoke + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(er_results_int)

@@

lrti_summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_total),
         lrti_events_num = lrti_events_num - 1) %>%  
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)

@@

int_function(analysis_data, "child_age")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

# Try child_age, gender, residents_smoke
```

@@

er_results_at_home <- er_results <- glmer(lrti_events_di_total ~ pm_mean_at_home_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_results_at_home, paste0(file_path, "Output/er_results_at_home.rds"))

er_winter1_results <- er_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk_winter +
                          (1 | cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_winter1_results, paste0(file_path, "Output/er_winter1_results.rds"))

er_burn_level_results <- er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          burn_level_3level + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_burn_level_results, paste0(file_path, "Output/er_burn_level_results.rds"))

er_home_size_results <- er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          home_sqft_2level + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_home_size_results, paste0(file_path, "Output/er_home_size_results.rds"))

er_stove_grade_results <- er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          stove_grade_3level + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_stove_grade_results, paste0(file_path, "Output/er_stove_grade_results.rds"))

er_stove_age_results <- er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          stove_age_3level + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + residents_smoke +
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
write_rds(er_stove_age_results, paste0(file_path, "Output/er_stove_age_results.rds"))
```

```{r}
# Load results
er_results <- read_rds(paste0(file_path, "Output/er_results.rds"))
er_results_at_home <- read_rds(paste0(file_path, "Output/er_results_at_home.rds"))
er_winter1_results <- read_rds(paste0(file_path, "Output/er_winter1_results.rds"))
er_burn_level_results <- read_rds(paste0(file_path, "Output/er_burn_level_results.rds"))
er_home_size_results <- read_rds(paste0(file_path, "Output/er_home_size_results.rds"))
er_stove_grade_results <- read_rds(paste0(file_path, "Output/er_stove_grade_results.rds"))
er_stove_age_results <- read_rds(paste0(file_path, "Output/er_stove_age_results.rds"))

@@

# Run results through function, save, combine for plotting
er_tidy <- results_function(er_results, "ER Primary")
er_at_home_tidy <- results_function(er_results_at_home, "ER PM at-home")
er_winter1_tidy <- results_function(er_winter1_results, "ER Winter 1 only")
er_burn_level_tidy <- results_function(er_burn_level_results, "ER + burn level")
er_home_size_tidy <- results_function(er_home_size_results, "ER + home size")
er_stove_grade_tidy <- results_function(er_stove_grade_results, "ER + stove grade")
er_stove_age_tidy <- results_function(er_stove_age_results, "ER + stove age")

# Combine cleaned results
er_results_combined <- rbind(er_tidy, er_at_home_tidy, er_winter1_tidy, er_burn_level_tidy, 
                              er_home_size_tidy, er_stove_grade_tidy, er_stove_age_tidy)
